\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-25 paper.tex
add explanation of HMC

Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
A set of samples are generated to approximate the desired distribution.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.

>>>>

Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $ .
A set of samples are generated to approximate the desired distribution $ \pi (x) $.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.
The concept origins from Hamiltonian dynamics, which models the movement of an object.
Given the position $ x $ and the momentum $ q $ of an object, the system energy can be written as $ H(x,q) = U(x) + K(q) $, in which $ U(x) $ is the potential energy and $ K(q) $ is the kinetic energy.
The movement of the object (how $ x $ and $ q $ change over time) is determined by
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
By the association between energy and a canonical distribution, a joint distribution for the states $ x $ and $ q $ can be created from a Hamiltonian dynamics, which is 
$ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
If we define $ U(x) = - \log ( \pi(x) T ) $, $ P(x, q) $ can be rewritten as $ P(x, q) = \pi (x) \frac{1}{Z} \exp (-K(q) / T) $.
Because the state $ x $ and the the momentum  $ q $ are independent, we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable).
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints.
